Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England

### 2021-09-01 analysis/report/draft-manuscript.Rmd
remove dodgy CIs for risk difference

  riskdifference <- 
    cmlinc  %>%
    group_by(model, model_name, outcome, outcome_descr, tstop) %>%
    arrange(tstop, model, outcome, vax1_az) %>%
    mutate(
      diff = (1-survival) - first((1-survival)),
      diff_format = label_number(0.01, scale=1000)(diff)
    ) %>%
    filter(vax1_az==1) %>%
    left_join(
      hazard %>% select(outcome, model, tstop, hr, hr.ll, hr.ul), 
      by=c("outcome", "model", "tstop")
    ) %>% 
    mutate(
      diff.ll = (1-survival) - (1-survival)*hr.ll,
      diff.ul = (1-survival) + (1-survival)*hr.ul
    ) #-(surv-lag(surv))/lag(surv)

  plot_riskdiff <-
    ggplot(riskdifference)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      limits = c(-5, 5),
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Risk difference\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

```{r comp,echo=FALSE, message=FALSE, out.width='90%', fig.height=8, results='asis'}
patchwork::wrap_plots(plot_cmlinc, plot_riskdiff, plot_hazard, ncol=1)
```

>>>>

  riskdifference <- 
    cmlinc  %>%
    group_by(model, model_name, outcome, outcome_descr, tstop) %>%
    arrange(tstop, model, outcome, vax1_az) %>%
    mutate(
      diff = (1-survival) - first((1-survival)),
      diff_format = label_number(0.01, scale=1000)(diff)
    ) %>%
    filter(vax1_az==1) %>%
    left_join(
      hazard %>% select(outcome, model, tstop, hr, hr.ll, hr.ul), 
      by=c("outcome", "model", "tstop")
    ) %>% 
    group_by(model, model_name, outcome, outcome_descr) %>%
    arrange(model, outcome, vax1_az, tstop) %>%
    mutate(
      hazard1 = -(survival - lag(survival, 1, 1)) / lag(survival, 1, 1),
      hazard0 = hazard1/hr,
      hazard0.ll = hazard1/hr.ul,
      hazard0.ul = hazard1/hr.ll,

      survival0 = exp(-cumsum(if_else(is.na(hazard0), 0, hazard0))),
      survival0.ll = exp(-cumsum(if_else(is.na(hazard0.ul), 0, hazard0.ul))),
      survival0.ul = exp(-cumsum(if_else(is.na(hazard0.ll), 0, hazard0.ul))),

      diff2 = (1-survival)-(1-survival0),

      diff.ll = (1-survival) - (1-survival)*hr.ll,
      diff.ul = (1-survival) + (1-survival)*hr.ul,
      #diff_CI = paste0(label_number(0.01, scale=1000)(diff), " (", diff.ll, " ,", diff.ul, ")")
    )

  plot_riskdiff <-
    ggplot(riskdifference)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    # geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      limits = c(-5, 5),
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Risk difference\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

```{r comp,echo=FALSE, message=FALSE, warnings=FALSE, out.width='90%', fig.height=8, results='asis'}
patchwork::wrap_plots(plot_cmlinc, plot_riskdiff, plot_hazard, ncol=1)
```
